\scuba: iterative map-making with the Sub-Millimetre User Reduction Facility

### 2012-09-03 smurf_paper.tex
more COM changes

The common-mode value at each time slice is calculated as the unweighted
mean of the values of all bolometers that have not previously been
flagged as bad. Thus, aberrant bolometers with low correlation
coefficients will be included, polluting the common-mode. By default, no
attempt is made to exclude these aberrant bolometers\footnote{An option
exists to reject unusually high or low bolometer values when calculating
the common mode value at each time slice, but this seems to introduce
instability into the convergence process and makes little difference to
the final maps.}.

Bolometer values that were flagged as poorly correlated with the common
mode on the previous iteration are nevertheless included in the
calculation of the common mode on the next iteration. If sensitivities
are allowed to vary with time as described above, then poorly correlated
values will be flagged in blocks of - typically of 30 seconds duration.
Excluding such flagged blocks from subsequent estimates of the common
mode can result in discontinuities in the common mode signal at the
edges of these blocks. This in turn can lead to ringing in the low pass
filter, and instabilities in the convergence process.

>>>>

The common-mode value at each time slice is calculated as the unweighted
mean of the values of all bolometers that have not previously been
flagged as bad for some other reason. Bolometer values that were flagged
as bad simply because they were poorly correlated with the common-mode on
the previous iteration are included in the new common-mode estimate. If
such samples are excluded, there is a strong possibility of
discontinuities appearing in the COM model at block boundaries.
These in turn can lead to ringing in the low pass filter, and
instabilities in the convergence process.
